% 20 Apr 2014 : GWA : 1 page.

\section{Introduction}
\label{sec-introduction}

As smartphones become ubiquitous, it is natural to expect to have access to
all of your personal content from these powerful devices---to view all of
your photos and videos; play any track from your music collection; and browse
through all of your previously sent chats, texts, and emails. All of these
use cases require smartphones to efficiently access far more data than they
can store locally, and yet both existing cloud storage
solutions~\cite{dropbox, googledrive} and recent research filesystem
designs~\cite{mashtizadeh2013replication, peek2006ensemblue} require each
client store a complete replica. As users assemble clouds of personal
devices---including smartphones, tablets, laptops, and desktops---that
collectively contain large amounts of storage, their storage capacity should
not be bottlenecked by the most storage-constrained device. Given the cost
and energy consumption of flash storage we do not anticipate mobile device
storage capacity to keep pace with other types of devices.

To address this personal storage bottleneck we propose to allow users to
apply the same techniques used to build reliable cloud storage to create
\textit{personal storage clouds}. By combining available space on existing
personal devices, personal storage clouds can achieve a capacity far greater
than offered by free cloud storage tiers. By utilizing nearby personal
devices, personal storage clouds can provide better performance than cloud
storage. And by applying modern approaches to reliability and availability,
personal storage clouds can cope with failures and disconnections inherent to
personal devices.

We present the design and implementation of PocketLocker, a system enabling
scalable, reliable, and performant personal storage clouds (PSC). PocketLocker is
designed to store rarely-changed files, such as photos, music, and videos,
and to provide access to an entire personal storage cloud from any client
device. PocketLocker exploits the locality of devices within the PSC
to arrange rapid transfers over local-area networks when
possible, and includes several energy-saving features to reduce battery
drain on battery-powered mobile clients. While PocketLocker uses direct
interaction between clients, it does not attempt to address the difficulties
of building a true peer-to-peer distributed storage system. Instead, a cloud
service called the \textit{orchestrator} is used to maintain a consistent
namespace and ensure that backup and availability requirements are met.
Clients apply local data caching policies that reflect their usage patterns
and their interaction with other clients. PocketLocker simplifies
locating data within the personal storage cloud by utilizing Reed-Solomon
erasure coding~\cite{reed1960polynomial}, allowing clients to reconstruct files as
long as they can acquire any set of mutually-redundant chunks.

Our paper makes the following contributions. First, we examine one month of
data from 100~users to better understand smartphone file access patterns. We
conclude that today's users are generating and accessing far more content
than can be stored directly on their mobile device, making file systems which
require each client to store a complete replica unusable. However, a survey
that we distributed to 47~people indicates that users do have free storage on
other personal devices. These results motivate PocketLocker's design.

Second, we present the design of PocketLocker and describe how it uses
multiple personal devices to build scalable, performant, and energy-efficient
personal storage clouds to store rarely-changed files such as music, videos,
and photos. PocketLocker uses erasure coding to divide files into multiple
chunks which are distributed across all the users' participating devices---which
can include smartphones, tablets, laptops, desktops, and dedicated storage
appliances. PocketLocker’s orchestrator, which runs as a cloud service,
distributes chunks across the users’ personal devices to maintain file
availability, maximize performance, and meet configurable backup
requirements.

Finally, we perform a detailed evaluation of PocketLocker that proceeds along
two lines. First, we utilize our file access traces to examine the impact of
several key PocketLocker design parameters and estimate the performance of
file access on PocketLocker. Second, we measure the energy consumption and
performance of an Android prototype as it accesses files under a variety of
real-world conditions. Our results confirm that by locating files
intelligently, PocketLocker can provide mobile users with energy-efficient
low-latency access to far more content than their mobile device can store
locally.

Our paper is structured as follows. Section~\ref{sec-motivation} presents
several results that motivate and inform PocketLocker's design, which we
present in detail in Section~\ref{sec-design}.
Section~\ref{sec-implementation} briefly describes the implementation of our
current PocketLocker prototype for Android smartphones, which we evaluate in
Section~\ref{sec-evaluation}. Section~\ref{sec-related} compares PocketLocker
to similar systems before Section~\ref{sec-conclusion} discusses future work
and concludes the paper.
